---
title: "iceburg"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Project Vinette

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(iceberg)
library(ggplot2)
library(dplyr)
library(readr)
```

## Introduction

In this Vignette, I will be explaining the two functions that make up the bulk of this package's functionality, ggplot_theme() and [Insert Name of Helper Function Here], as well as demostrating how to use this two packages and what their end products will look like

## Dataset: MODIS Thermal Anomilies in Australia and New Zealand

For the purpose of showcasing this package, I have chosen the data set named "MODIS_C6_Australia_and_New_Zealand_7d.csv". This dataset contain information on thermnal anomiles (fires) detected by NASA's MODIS satellite that have occurred within a seven day period. Documentation can be found at this [link](https://github.com/rfordatascience/tidytuesday/blob/main/data/2020/2020-01-07/readme.md)

```{r}
MODIS_data = read_csv("MODIS_C6_Australia_and_New_Zealand_7d.csv")
```

## Demonstrate iceberg_theme()

This theme was developed with the idea that it would replicate the color scheme and feel of an iceberg. This package will be used to develop other visualizations through the course of the semester.

Then we will make a graph using our MODIS_data data frame. This graph will seek to find if their is a difference between the distribution of thermal anomaly brightness by whether or not it was observed during the day or the night. 

```{r}
# sample ggplot_graph for testing purposes
ggplot(MODIS_data, aes(x = daynight, 
                          y = brightness)) +
  geom_boxplot() +
  labs(title = "Distrbution of Thermal Anomily Brightness by Day and Night",
       x = "Day or Night", 
       y = "Brightness (Kelvin)") +
  iceberg_theme()
```

# Demonstrate scale_color_gradient_iceberg

Let's create a scatter plot which will use the custom scale_color_gradient() function. Because we have latitude and longitiude data, we can use this to create a rough map. 

```{r}
ggplot(MODIS_data, aes(x = latitude, 
                       y = longitude, 
                       color = brightness)) +
  geom_point() + 
  iceberg_theme() +
  scale_color_gradient_iceberg() + 
  labs(
    title = "Heatmap of Brightness of Individual Thermal Anomlies in Kelvin", 
    x = "Latitude",
    y = "Longitiude"
  )
```

# Demonstrate scale_fill_iceberg()

Now let us create a plot which will detail a use case for the scale_fill_iceberg() function. This function can be added onto any plot which uses the fill argument in it's aesthetics. For geom_point it might be necessary to include the arguement "shape = fill"

```{r}
ggplot(MODIS_data, aes(x = brightness, 
                       y = frp, 
                       fill = daynight)) +
  geom_point(shape = 21) +
  iceberg_theme() +
  scale_fill_iceberg() +
  labs(title = "Brightness by FFP")
```

# Demonstrate full_count_proportion

We can use this function to get the proportion of a number category in a data set.

```{r}
MODIS_data %>%
  full_count_proportion(., column_name = longitude) %>%
  select(longitude, latitude, prop)
```

# Five Data Moves

Using our data we will go through the five data moves in order to fully understand an aspect of our dataset

## Group

We will group by the daynight logical and the satellite logicall. daynight indicates if the fire occured in the day or the night, and satellite indicates which of satellite

```{r}
MODIS_data_moves = MODIS_data %>%
  group_by(daynight, satellite)
```

## Filter

For this data move we will filter by version of the satellite which was

```{r}
MODIS_data_moves = MODIS_data_moves %>%
  filter(version == "6.0NRT")
```

## Calculating

For this section we will calculate the total brightness

```{r}
MODIS_data_moves = MODIS_data_moves %>%
  mutate(total_brightness = sum(brightness))
```

## Summarizing

Our group by from earlier will help us get the total count of each satellite's day and night observations

```{r}
MODIS_data_moves %>%
  summarize(total = n())
```

## Hierarchy

Each satellite has it's own version associate to it, with multiple versions, therefore we can group the data first by satellite, and then by 

```{r}
MODIS_data_moves %>%
  group_by(satellite, version) %>%
  select(satellite, version)
```

## Merging

I tried to find a data frame that would map to this, I was unsuccessful... so I made my own! I also have to assign a identifier to every row in the original data set, but now we can merge. 

```{r}
n = nrow(MODIS_data)

new_df = data.frame(
  id = 1:n,
  number = runif(n)
)


MODIS_data = MODIS_data %>%
  mutate(id = 1:n)

MODIS_data %>%
  left_join(new_df, by = "id")
```


