---
title: "package_project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Project Vinette

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
```

## Introduction

In this Vignette, I will be explaining the two functions that make up the bulk of this package's functionality, ggplot_theme() and [Insert Name of Helper Function Here], as well as demostrating how to use this two packages and what their end products will look like

## Dataset: MODIS Thermal Anomilies in Australia and New Zealand

For the purpose of showcasing this package, I have chosen the data set named "MODIS_C6_Australia_and_New_Zealand_7d.csv". This dataset 
contain information on thermnal anomiles (fires) detected by NASA's MODIS satellite that have occurred within a seven day period. 

```{r}
MODIS_data = read_csv("MODIS_C6_Australia_and_New_Zealand_7d.csv")
```

## ggplot_theme()

This theme is developed with the idea that it will be used for every single visualization I make in the future, it will include changes to the font and the colors in the graph in order to personalize and adapt it to my style. 

First we load in the our package

```{r}
library(package_project)
```

Then we will make a graph using our MODIS_data dataframe. This graph will seek to find if their is a difference between the two 

```{r}
MODIS_data_brightness = MODIS_data %>%
  group_by(daynight) %>%
  summarise(avg_brightness = median(brightness))

# sample ggplot_graph for testing purposes
ggplot(MODIS_data, aes(x = daynight, 
                          y = brightness)) +
  geom_boxplot() +
  labs(title = "Average Thermal Anomily Brightness by Day and Night",
       x = "Day or Night", 
       y = "Mean Brightness") +
  iceberg_theme()
```


