---
title: "package_project"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{package_project}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Package Project Vinette

```{r, include = FALSE, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(tidyverse)
```

## Introduction

In this Vignette, I will be explaining the two functions that make up the bulk of this package's functionality, ggplot_theme() and [Insert Name of Helper Function Here], as well as demostrating how to use this two packages and what their end products will look like

## Dataset: MODIS Thermal Anomilies in Australia and New Zealand

For the purpose of showcasing this package, I have chosen the data set named "MODIS_C6_Australia_and_New_Zealand_7d.csv". This dataset contain information on thermnal anomiles (fires) detected by NASA's MODIS satellite that have occurred within a seven day period. Documentation can be found at this [link](https://github.com/rfordatascience/tidytuesday/blob/main/data/2020/2020-01-07/readme.md)

```{r}
MODIS_data = read_csv("MODIS_C6_Australia_and_New_Zealand_7d.csv")
```

## Demonstrate iceberg_theme()

This theme was developed with the idea that it would replicate the color scheme and feel of an iceberg. This package will be used to develop other visualizations through the course of the semeseter.

```{r}
library(package_project)
```

Then we will make a graph using our MODIS_data dataframe. This graph will seek to find if their is a difference between the distribution of thermal anomaly brightness by whether or not it was observed during the day or the night. 

```{r}
# sample ggplot_graph for testing purposes
ggplot(MODIS_data, aes(x = daynight, 
                          y = brightness)) +
  geom_boxplot() +
  labs(title = "Distrbution of Thermal Anomily Brightness by Day and Night",
       x = "Day or Night", 
       y = "Brightness (Kelvin)") +
  iceberg_theme()
```

# Demonstrate scale_color_gradient_iceberg.R

Let's create a scatter plot which will use the custom scale_color_gradient() function. Because we have latitude and longitiude data, we can use this to create a rough map. 

```{r}
ggplot(MODIS_data, aes(x = latitude, 
                       y = longitude, 
                       color = brightness)) +
  geom_point() + 
  iceberg_theme() +
  scale_color_gradient_iceberg()
```
